Curriculum and Imitation Learning for Biped Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
Updates to no-curriculum-baseline section

In this section, we evaluate CIM against a baseline that does not use curriculum learning.
Instead, the baseline begins training in the final, most difficult testing environment.
Results are shown in Fig. \ref{fig:nocur baseline}.

>>>>

In this section, we evaluate CIM against a baseline that does not use curriculum learning.
Instead, the baseline begins training with a quadratic model in the final, most difficult testing environment.

Due to the sample complexity of the quadratic model, making this a fair comparison requires changing the training schedule used for imitation learning.
For the CIM experiments, we retrained the model every four rollouts,
but with a quadratic model this leads to disastrous overfitting and actually makes the expert \emph{worse}.
We tried several alternative imitation learning schedules.
Best results for the baseline were obtained by collecting an initial dataset of 32 rollouts and thereafter retraining every 16 rollouts.
Hyperparameters for the baseline were otherwise identical to the ones used for CIM.

Results on the 2D-Hard environment are shown in Fig. \ref{fig:nocur baseline}.
Like in Fig. \ref{fig:rs baseline},
we plot the median reward and 5th/95th percentiles over 32 testing episodes.

Even without a curriculum, the algorithm is able to find a policy that \emph{usually} achieves high reward.
However, CIM reaches the same median performance twice as quickly.
The story is similar for fifth-percentile performance.
\nhatch{TODO finish this once rerunning experiments finish}
